---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
    collapse = TRUE,
    comment = "#>",
    dev = 'svglite',
    fig.path = "man/figures/README-",
    fig.showtext = TRUE,
    fig.width = 6.377953,
    fig.height = 3.93701,
    out.width = "100%"
)
```

# reactor

<!-- badges: start -->
<!-- badges: end -->

An R package for simulating reaction and reaction-diffusion systems.

## Installation

You can install the development version from [GitHub](https://github.com/) with:

```r
devtools::install_github("dbarrows/reactor")
```

## Reaction system solvers

Networks are created using the [`bondr`](https://github.com/dbarrows/bondr) package. See [Creating Networks](https://github.com/dbarrows/bondr#creating-networks) for more details.

```{r}
library(reactor)

(mm_network <- parse_network(bondr::mm_string))
```

### RRE

A deterministic solver that uses the Reaction Rate Equation (RRE) in conjunction with an ode solver.

```{r}
(model <- rmodel(network = mm_network,
                 state = c(301, 120, 0, 0),
                 tspan = c(0, 30)))
```
```{r}
(sol <- rre(model))
```

A function is provided for easy visualisation of solutions.

```{r}
rsol_plot(sol)
```

### SSA

Generate a single realisation of the Chemical Master Equation (CME) solution via the Stochastic Solution Algorithm (SSA).

```{r}
ssa(model) %>%
    rsol_plot()
```

## Reaction-diffusion system solvers

Reaction-diffusion models created via the `rdmodel` class, which are constructed similarly to `rmodel`s.

```{r}
(model <- rdmodel(
    network = parse_network("
             0 <-> U,  4e3, 2
             0  -> V,  1.2e4
        2U + V  -> 3U, 12.5e-8
    "),
    volume = volume(
        dims = c(40, 1, 1),
        h = 1/40,
        seed = c(25, 75)
    ),
    D = c(1e-3, 1e-1),
    tspan = c(0, 3.5)
))
```

### ISSA

Generate a single realisation of the Reaction-diffusion Master Equation (RDME) solution via the Inhomogeneous Stochastic Solution Algorithm (ISSA).

```{r}
issa(model) %>%
    rdsol_plot()
```

