---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
    collapse = TRUE,
    comment = "#>",
    dev = 'svglite',
    fig.path = "man/figures/README-",
    fig.showtext = TRUE,
    fig.width = 6.377953,
    fig.height = 3.93701,
    out.width = "100%"
)
```

# reactor

<!-- badges: start -->
<!-- badges: end -->

An R package for simulating reaction and reaction-diffusion systems.

## Installation

You can install the development version from [GitHub](https://github.com/) with:

```r
devtools::install_github("dbarrows/reactor")
```

## Reaction system solvers

Networks are created using the [`bondr`](https://github.com/dbarrows/bondr) package. See [Creating Networks](https://github.com/dbarrows/bondr#creating-networks) for more details.

```{r}
library(reactor)

(mm_network <- parse_network(bondr::mm_string))
```

#### RRE

A deterministic solver that uses the Reaction Rate Equation (RRE) in conjunction with an ode solver.

```{r}
(model <- rmodel(network = mm_network,
                 state = c(301, 120, 0, 0),
                 tspan = c(0, 30)))
```
```{r}
(sol <- rre(model))
```

A function is provided for easy visualisation of solutions.

```{r}
rsol_plot(sol)
```

#### SSA

Generate a single realisation of the Chemical Master Equation (CME) solution via the Stochastic Solution Algorithm (SSA).

```{r}
ssa(model) %>%
    rsol_plot()
```
